Symmetric Circuits for Rank Gates

### 2018-02-05 sections/symmetric-circuits.tex
Feb 5

Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
\rho)$-circuit of order $n$ and let $g \in G$. We say a gate $g \in G$ is a
\emph{symmetric gate} if $\Sigma(g)$ is a symmetric function. We say a gate $g
\in G$ is a \emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric
structured function. We say that $g$ is an \emph{$\AND$ gate} if $\Sigma(g) :=
\land [a]$ for some $a \in \nats$. Similarly we define \emph{$\OR$- gates},
\emph{$\NOT$ gates}, \emph{$MAJ$ gates} and \emph{$\rank$ gates}.

We say $C$ is a \emph{circuit with symmetric gates} if every gate in $C$ is
symmetric. We say $C$ is a \emph{matrix-circuit} if every gate in $C$ is
matrix-symmetric or symmetric. We say $C$ is a \emph{rank-circuit} if $C$ is a
matrix-circuit and every non-symmetric gate is a $\rank$ gate.

>>>>

Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
\rho)$-circuit of order $n$ and let $g \in G$. We say a gate $g \in G$ is a
\emph{symmetric gate} if $\Sigma(g)$ is a symmetric function. We say a gate $g
\in G$ is a \emph{matrix-symmetric gate} if $\Sigma(g)$ is a matrix-symmetric
structured function. We say that $g$ is an \emph{$\AND$-gate} if $\Sigma(g) :=
\land [a]$ for some $a \in \nats$. Similarly we define \emph{$\OR$-gates},
\emph{$\NOT$-gates}, \emph{$\MAJ$-gates} and \emph{$\rank$-gates}.

We say $C$ is a \emph{circuit with symmetric gates} if every gate in $C$ is
symmetric. We say $C$ is a \emph{matrix-circuit} if every gate in $C$ is
matrix-symmetric or symmetric. We say $C$ is a \emph{rank-circuit} if $C$ is a
matrix-circuit and every non-symmetric gate is a $\rank$-gate.
